The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-09 ms.tex
Changing figure somewhat

\begin{figure}
\includegraphics[width=\columnwidth]{cooling2.pdf}
\caption{\label{fig:cooling2} Ratio of heating rate to cooling rate
  $\rs$ versus $\Mbh$ for core ($\Gamma=0.1$) galaxies ({\it dashed})
  and cusp ($\Gamma=0.8$) galaxies ({\it solid}). Ratio is calculated
  using equation~\eqref{eq:cooling2} and the results for $\vwO$ and
  $\eta$ in Figures~\ref{fig:vwSources} and~\ref{fig:eta}}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{rs_rIa.pdf}
\caption{\label{fig:rs_rIa} $\rIa/\rs$ vs. $\Mbh$. $\rIa$ is
  calculated using equation~\eqref{eq:rIa} {\bf AG: I am just
    referring to the first part of the equation here--I use the
    appropriate convolution the Ia rate here}. $\rs$ is calculated
  using the equation~\eqref{eq:stag_simple} and the $\vwO$
  corresponding to each $\Mbh$--see Figure~\ref{fig:vwSources}. For
  the blue curve we use the total $\vwO$ from stars, MSP, and
  black hole feedback (e.g. the solid black curve in
  Figure~\ref{fig:vwSources}). For the purple curve we also include
  the $\vwO$ from Ia's (the dashed red curve
  Figure~\ref{fig:vwSources}).}
\end{figure}

>>>>

% \begin{figure}
% \includegraphics[width=\columnwidth]{cooling2.pdf}
% \caption{\label{fig:cooling2} Ratio of heating rate to cooling rate
%   $\rs$ versus $\Mbh$ for core ($\Gamma=0.1$) galaxies ({\it dashed})
%   and cusp ($\Gamma=0.8$) galaxies ({\it solid}). Ratio is calculated
%   using equation~\eqref{eq:cooling2} and the results for $\vwO$ and
%   $\eta$ in Figures~\ref{fig:vwSources} and~\ref{fig:eta}}
% \end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{rs_rIa.pdf}
\caption{\label{fig:rs_rIa} $\rIa/\rs$ vs. $\Mbh$. $\rIa$ is
  calculated using equation~\eqref{eq:rIa} {\bf AG: I am just
    referring to the first part of the equation here--I use the
    appropriate convolution the Ia rate here}. $\rs$ is calculated
  using the equation~\eqref{eq:stag_simple} and the $\vwO$
  corresponding to each $\Mbh$--see Figure~\ref{fig:vwSources}. For
  the blue curve we use the total $\vwO$ from stars, MSP, and
  black hole feedback (e.g. the solid black curve in
  Figure~\ref{fig:vwSources}).}
\end{figure}

### 2015-02-09 windheat.tex
Changing figure somewhat

\begin{figure}
\includegraphics[width=\columnwidth]{vwImp.pdf}
\caption{\label{fig:vwImp} The effective heating rate, $\vw^{\star}$, from stellar winds from
  a stellar population of age $\tau_{\star}$.  {\bf BDM: change axis label to $\tau_{\star}$}}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{etaImp.pdf}
\caption{\label{fig:etaImp} The mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), resulting from stellar winds from
  a stellar population of age $\tau_{\star}$.  {\bf BDM: change axis label to $\tau_{\star}$}}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{vwImp.pdf}
\caption{\label{fig:vwImp} The effective heating rate, $\vw^{\star}$, from stellar winds from
  a stellar population of age $\tau_{\star}$.}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{etaImp.pdf}
\caption{\label{fig:etaImp} The mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), resulting from stellar winds from
  a stellar population of age $\tau_{\star}$.}
\end{figure}
